% Cover letter using letter.sty
\documentclass[11pt]{letter}
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
%\topmargin=-1in    % Make letterhead start about 1 inch from top of page
%\textheight=8in  % text height can be bigger for a longer letter
%\oddsidemargin=0pt % leftmargin is 1 inch
%\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
%\bottommargin=1in

\def \myname {Alexander McGinnis}
\def \myemail {mcginnisalexander@gmail.com}
\def \theirname {Hiring Team}




\usepackage[top=0.7in, left=0.7in, bottom=0.7in, right=0.7in]{geometry}
\usepackage{qrcode}
\usepackage{verbatim}
\usepackage{fontspec}

%\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
%\setmainfont{IBM Plex Serif Text}
% \setmonofont{Lucida Sans Typewriter}


\begin{document}

\signature{\myname}           % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left


\begin{letter}{\theirname \\
%Senior Staff Recruiter \\
Keysight Technologies \\
1400 Fountaingrove Parkway \\
Santa Rosa, CA 95403
}


\begin{flushleft}
{\large\bf \myname}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill \myemail \\
\hfill (707) 583-9017 \\
%\qrcode[height=2cm]{\myemail} \\
\end{flushright}
%\vfill % forces letterhead to top of page


\opening{Dear \theirname :}


I developed a passion for RF testing and research during my experience at a navy laboratory, where I participated in several related projects there, the most notable of which are summarized in my resume. I feel comfortable with RF instruments, such as FieldFoxes, other vector network analyzers and automating tests with various equipment in LabView.

I have toured the Santa Rosa campus, and my glimpse at the workplace culture and atmosphere made me eager to start a career there. I am inspired by how much manufacturing is still done domestically at Keysight. I can envision myself at Keysight for the length of my career.

I have spent a lot of time using Keysight or Agilent branded radio frequency (RF) instruments, and I have come to appreciate the attention to detail in the overall user experience of Keysight products. These are qualities I pay a lot of attention to in consumer electronics that I use, and most of the time I find them to be lacking or frustrating, and spend a long time tweaking them myself if I can. For example, one of my hobbies is building mechanical PC keyboards, and I love to perfect key layers in the firmware.

When it comes to research, I contributed to a larger project by characterizing and redesigning a power amplifier output filter bank to switch bands faster. The project sought to improve frequency hopping techniques in High Frequency (HF) band equipment using nascent high power semiconductor technology. I also wrote software to automate antenna pattern measurements in a generalizable way in MATLAB. This software generated layman-readable reports using raw vector network analyzer data of calibration antennas, and the numerous antennas of interest.

I have successfully worked with small groups to complete projects numerous times. I started working with groups to solve technical challenges during my experience with high school competitive robotics, and I thrive in collaborative situations. I have worked with a five person team for a political voter data analysis project, and I am working with a three person team on my year-long senior design project. During my internships I was given the opportunity to collaborate with several individuals or teams in order to contribute to larger scale projects.





\closing{Sincerely yours,}



%\encl{}  				% Enclosures

\end{letter}


\end{document}
